### 2014-08-31 fundamentals/impl.tex
dynamically loadable libraries implementation section closely follows katy's dissertation discussion on this topic. Some slight paraphrasing was employed to avoid self-plaigarism

\subsection{Dynamically loadable libraries}
% (diagram)

A key innovation that has previously not been implemented in nuclear fuel cycle 
simulators in the literature is implementing this generic API and modular 
architecture into a suite of dynamically loadable ``plug-in'' libraries.

This approach allows contribution to an ecosystem of libraries. The 
scientist-developer can therefore focus on generating a model within their 
sphere of expertise, while relying on the model contributions of others to fill 
in the other technologies.

This is implemented largely through a clean API and a modern build system.

>>>>

\subsection{Dynamically Loadable Libraries}
% (diagram)

A key innovation that has previously not been implemented in nuclear fuel cycle 
simulators in the literature is implementing this generic API and modular 
architecture into a suite of dynamically loadable ``plug-in'' libraries. 
This is implemented largely through a clean API and a modern build system.

Dynamically-loadable libraries are the primary mechanism for extending \Cyclus' capability. 
This approach provides encapsulation: the core of the code operates
completely independently from the individual libraries. Thus, any
customization or extension is implemented only in the loadable
library.

This approach allows efficient, targeted contribution to the ecosystem of libraries.  The 
scientist-developer can therefore focus on generating a model within their 
sphere of expertise, while relying on the model contributions of others to fill 
in the other technologies.  This strategy also allows individual developers to
explore different levels of complexity within their archetypes, including
wrapping other simulation tools as loadable libraries within the \Cyclus
framework.

A secondary benefit is the ability for
contributors to choose different distribution and licensing strategies
for their contributions. By allowing models to have varied
availability, the security concerns of developers can be
assuaged (See Figure \ref{fig:modifiedopen}).

\begin{figure}[htbp!]
\begin{center}
\includegraphics{./images/modifiedopen.eps}
\end{center}
\caption{The \Cyclus framework enables fully open, partially open, and fully
closed collaborations\cite{wilson_cyclus:_2012}.}
\label{fig:modifiedopen}
\end{figure}

In particular, since the clean plug-in architecture loads libraries without any
modifications to the \Cyclus kernel, closed-source archetypes can be used with
the simulator alongside open-source archetypes. This architecture therefore
allows closed-source libraries (e.g., those representing sensitive nuclear
processes and subject to export control) to be developed and licensed privately.

This last benefit of dynamically-loadable libraries addresses
another goal of \Cyclus: ubiquity amongst its potential user base. By
engineering \Cyclus to easily handle varying levels of complexity, a single
simulation engine can be used by both users interested in big-picture policy
questions as well as users focused on more detailed, technical
analyses.
